In-Rank mesh optimization for URL customized promotion in SEO

### 2015-03-03 MY_PAPERS/article_sduprey_iswag_02_06_2014.tex
iswag

We here choose genetic algorithms among others. Simulated annealing, global search, multistart, particle swarm have been tested and also works on the small case to be presented.

@@

Genetic algorithm is a search heuristic that mimics the process of natural selection. 

@@

First we compute the standard page rank of the individual matching mesh :

@@

\begin{center}
\textbf{\large Population at convergence}
\end{center}
\begin{center}
\epsfig{file=converged_population.eps,height=5cm,width=5cm}
\end{center}
\begin{center}
\textbf{\large Best chromosome fitness function evolution}
\end{center}
\begin{center}
\epsfig{file=best_element_evolution.eps,height=5cm,width=5cm}
\end{center}
\section{An e-commerce approach}
For an e-commerce web site, traffic might not always coincide with the URLs you deem as more profitable to you.
On the very contrary, you may even actually rather want to rebalance some traffic discrepancies.
Of course, the methodology presented above is still valid. You here just have to change the importance vector you want to
optimize. In that case, you would for instance rather optimize $\frac{1}{traffic\left(i\right)}$.
\\\newline
But to get a real sense of potential return on investment, we must here switch to a new paradigm.
Each page will be matched with a specific keywords expression to rank upon. And the potential return on investment for the keywords expression will
be assessed with both search engine data (click through rate, search volume) and e-commerce tracking data (transformation rate).
To push potentially high return on investment pages, we use the following objective function :
\begin{equation}
 \sum_{i\in Keywords} SV\left( i\right)\times CTR\left(position\left(i\right)\right)\times CR\left(i\right)\times P\left(i\right)
\end{equation}
where $position\left(i\right)$ is the estimated position in search engine results coming from the modification of our new mesh,
\\\newline
$SV\left(i\right)$ is the search volume for the keywords $i$ estimated by the search engine.
\\\newline
and $CTR\left(i\right)$ is the click through rate for an URL at the position place in the search engine results.
\\\newline
The difficult part here is how to estimate the new position in search engine results for our new mesh.
This is here hardly conceivable to imagine a feed-back loop with a real search engine indexation. This would drastically
slow our algorithm. The best approach here is to build and etalonnate a machine learning algorithm to model the relationship between local in-rank $PR\left(i\right)$
and $position(i)$.
\\\newline
One last remark here about a possible enhancement to our algorithm. As most e-commerce web sites tend to overlink web pages between themselves, 
we could add a supplementary weigh to our optimization formula to rebalance link according to their semantic reliability.
\begin{equation}
\max_{\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}}\left\{ \sum^{N}_{i=1} CS\left(i\right)\times f\left(X_i\right)\times PR(X_i)\right\}
\end{equation}
where $CS(i)$ is a semantic distance between the two linked pages by $i$, for instance the cosinus of Salton. 
\section{Big data implementaion}
The double iterative nature of our algorithm (page rank computations and optimization are both naturally iterative)
makes Hadoop Map/Reduce paradigm too slow for our purpose. 
\\\newline
In contrast to Hadoop's two-stage disk based Map/Reduce paradigm, Spark's in-memory primitives provide the needed performance.
By allowing user programs to load data into a cluster's memory and query it repeatedly, Spark is well suited for our purpose.
We'll detail the technological implementation of a real-world use case.

The in rank fitness function is computed recurrently over the whole population. To improve its performance is key for an efficient
algorithm. The idea here would be to computed an approximated in rank with a faster function using \cite{}.

>>>>

We here choose genetic algorithms among others following here \cite{gen_algo_web}. Simulated annealing, global search, multistart, particle swarm have been tested and also works on the small case to be presented.

@@

Genetic algorithm is a search heuristic that mimics the process of natural selection as explained in \cite{gen_algo}. 

@@

First we compute the standard page rank of the individual matching mesh following \cite{page_rank} :

@@

\textbf{\large Population at convergence}
\epsfig{file=converged_population.eps,height=5cm,width=5cm}
\textbf{\large Best chromosome fitness function evolution}
\epsfig{file=best_element_evolution.eps,height=5cm,width=5cm}
The structure found is as we expected : home followed by metalists, lists and then products.

\section{An e-commerce approach}
For an e-commerce web site, traffic might not always coincide with the URLs you deem as more profitable to you.
On the very contrary, you may even actually rather want to rebalance some traffic discrepancies.
Of course, the methodology presented above is still valid. You here just have to change the importance vector you want to
optimize. In that case, you would for instance rather optimize $\frac{1}{traffic\left(i\right)}$.
\\\newline
But to get a real sense of potential return on investment, we must here switch to a new paradigm.
Each page will be matched with a specific keywords expression to rank upon. And the potential return on investment for the keywords expression will
be assessed with both search engine data (click through rate, search volume) and e-commerce tracking data (transformation rate).
To push potentially high return on investment pages, we use the following objective function :
\begin{equation}
 \sum_{i\in Keywords} SV\left( i\right)\times CTR\left(position\left(i\right)\right)\times CR\left(i\right)\times P\left(i\right)
\end{equation}
where $position\left(i\right)$ is the estimated position in search engine results coming from the modification of our new mesh,
\\\newline
$SV\left(i\right)$ is the search volume for the keywords $i$ estimated by the search engine.
\\\newline
and $CTR\left(i\right)$ is the click through rate for an URL at the position place in the search engine results.
\\\newline
The difficult part here is how to estimate the new position in search engine results for our new mesh.
This is here hardly conceivable to imagine a feed-back loop with a real search engine indexation. This would drastically
slow our algorithm. The best approach here is to build and etalonnate a machine learning algorithm to model the relationship between local in-rank $PR\left(i\right)$
and $position(i)$ as in \cite{learning_to_rank}.
\\\newline
One last remark here about a possible enhancement to our algorithm. As most e-commerce web sites tend to overlink web pages between themselves, 
we could add a supplementary weigh to our optimization formula to rebalance link according to their semantic reliability.
\begin{equation}
\max_{\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}}\left\{ \sum^{N}_{i=1} CS\left(i\right)\times f\left(X_i\right)\times PR(X_i)\right\}
\end{equation}
where $CS(i)$ is a semantic distance between the two linked pages by $i$, for instance the cosinus of Salton. 
\section{Big data implementation}
We'll in this section detail the technological implementation of a real-world use case.

\\\newline
First, let's remark here that an easy and very efficient way to improve our algorithm performance would be to improve the in rank computing function. Its performance is key for an efficient algorithm, as it
is computed recurrently for each generation over all the population. The idea here would be to compute an approximated but faster in rank function as in \cite{page_rank_approx}.
\\\newline
The double iterative nature of our algorithm (page rank computations and global optimization are both naturally iterative)
makes Hadoop Map/Reduce paradigm in \cite{map_reduce} too slow for our purpose. 
In contrast to Hadoop's two-stage disk based Map/Reduce paradigm, Spark's in-memory primitives provide the needed performance (\cite{spark_methodo_bis} \cite{spark_methodo}).
By allowing user programs to load data into a cluster's memory and query it repeatedly, Spark is well suited for our purpose \cite{incremental_ram}
\cite{spark_bis_bis}.
\\\newline

Graph processing at scale from a graph database like Neo4j is a tremendously valuable power.
